Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2022-06-02 manuscript/manuscript.Rmd
Formatting requirements for manuscript submission

The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons. The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F). Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2) and \ref{tab:score-table-4}).

Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations) and \ref{fig:performance-locations-rel}).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \ref{fig:performance-locations-rel}A, \ref{fig:performance-locations-rel}G, \ref{fig:agg-performance-all-Germany}, \ref{fig:agg-performance-all-Poland}).

@@

Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model. In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively. An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions) in the SI.

@@

```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon. Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity). For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
```

>>>>

The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons. The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \ref{fig:agg-performance-all}F). Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).

Generally, trends in overall performance were broadly similar across locations (Figures \ref{fig:performance-locations} and \ref{fig:performance-locations-rel}).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \ref{fig:performance-locations-rel}A, \ref{fig:performance-locations-rel}G, \ref{fig:agg-performance-all-Germany}, \ref{fig:agg-performance-all-Poland}).

@@

Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model. In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on 28 December 2020 over the Christmas period) and a maximum of 10. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively. An overview of all models and ensemble versions is shown in Table \ref{tab:table-ensemble-versions} in the SI.

@@

```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon. Shown are the median, as well as the 50\\% and 90\\% prediction intervals (in order of decreasing opacity). For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
```

### 2022-06-02 manuscript/manuscript.tex
Formatting requirements for manuscript submission

The renewal model exhibited a noticeable tendency towards
over-predicting reported cases across all horizons. The crowd forecast
tended to over-predict at longer forecast horizons, whereas the Hub
ensemble showed no systematic bias (Figure
\ref{fig:agg-performance-all}F). Regardless of a general relative
tendency to over-predict, all forecasting approaches incurred larger
absolute penalties from over- than from under-prediction (see
decomposition of the WIS into absolute penalties for over-prediction,
under-prediction and dispersion in Figures
\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
Tables \textbackslash ref\{tab:score-table-2) and
\ref{tab:score-table-4}).

Generally, trends in overall performance were broadly similar across
locations (Figures \textbackslash ref\{fig:performance-locations) and
\ref{fig:performance-locations-rel}). Due to the differing population
sizes and numbers of notifications in Germany and Poland absolute scores
were difficult to compare directly. However, relative to the Hub
ensemble, the crowd forecasts performed noticeably better in Germany
than in Poland and the renewal model better in Poland than in Germany
(Figures \ref{fig:performance-locations-rel}A,
\ref{fig:performance-locations-rel}G,
\ref{fig:agg-performance-all-Germany},
\ref{fig:agg-performance-all-Poland}).

@@

Of our three models, only the renewal model and the crowd forecast were
included in the official Forecast Hub median ensemble
(``hub-ensemble-realised''), while the convolution model was never
included as it was deemed too similar to the existing renewal model. In
the official Hub ensemble, there were on average 7.1 models included
(including our own), with a median of 7, a minimum of 4 (on 28 December
2020 over the Christmas period) and a maximum of 10. Versions that
included either all of our models (``hub-ensemble-with-all'') or only
one of them (``hub-ensemble-with-X'') were computed retrospectively. An
overview of all models and ensemble versions is shown in Table
\textbackslash ref\{tab:table-ensemble-versions) in the SI.

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon. Shown are the 90\% and 50\% prediction intervals as well as the median (in order of increasing opacity). For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
\end{figure}

>>>>

The renewal model exhibited a noticeable tendency towards
over-predicting reported cases across all horizons. The crowd forecast
tended to over-predict at longer forecast horizons, whereas the Hub
ensemble showed no systematic bias (Figure
\ref{fig:agg-performance-all}F). Regardless of a general relative
tendency to over-predict, all forecasting approaches incurred larger
absolute penalties from over- than from under-prediction (see
decomposition of the WIS into absolute penalties for over-prediction,
under-prediction and dispersion in Figures
\ref{fig:agg-performance-all}A and \ref{fig:agg-performance-all}B and
Tables \ref{tab:score-table-2} and \ref{tab:score-table-4}).

Generally, trends in overall performance were broadly similar across
locations (Figures \ref{fig:performance-locations} and
\ref{fig:performance-locations-rel}). Due to the differing population
sizes and numbers of notifications in Germany and Poland absolute scores
were difficult to compare directly. However, relative to the Hub
ensemble, the crowd forecasts performed noticeably better in Germany
than in Poland and the renewal model better in Poland than in Germany
(Figures \ref{fig:performance-locations-rel}A,
\ref{fig:performance-locations-rel}G,
\ref{fig:agg-performance-all-Germany},
\ref{fig:agg-performance-all-Poland}).

@@

Of our three models, only the renewal model and the crowd forecast were
included in the official Forecast Hub median ensemble
(``hub-ensemble-realised''), while the convolution model was never
included as it was deemed too similar to the existing renewal model. In
the official Hub ensemble, there were on average 7.1 models included
(including our own), with a median of 7, a minimum of 4 (on 28 December
2020 over the Christmas period) and a maximum of 10. Versions that
included either all of our models (``hub-ensemble-with-all'') or only
one of them (``hub-ensemble-with-X'') were computed retrospectively. An
overview of all models and ensemble versions is shown in Table
\ref{tab:table-ensemble-versions} in the SI.

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth,]{../analysis/plots/comparison-forecast-interals} \caption{Crowd forecasts and baseline shown in the application for a two week horizon. Shown are the median, as well as the 50\% and 90\% prediction intervals (in order of decreasing opacity). For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons).}\label{fig:compare-forecasters}
\end{figure}
